An Empirical Analysis of the Role of Energy in Economic Growth

### 2014-05-18 Article/EconGrowth2-GraphsOnly.Rnw
Article now relies on re-leveling of factors by PostProcess.R

# Rearrange the country factors to obtain our preferred ordering.
coeffs_df$country <- as.factor(coeffs_df$country)
for (lev in rev(countryAbbrevs)) { coeffs_df$country <- relevel(coeffs_df$country, ref=lev) }
# Change the names of the energy factors to the names for the graph
coeffs_df$energy <- replace(coeffs_df$energy, which(is.na(coeffs_df$energy)), "none")
coeffs_df$energy <- replace(coeffs_df$energy, which(coeffs_df$energy=="iQ"), "q")
coeffs_df$energy <- replace(coeffs_df$energy, which(coeffs_df$energy=="iX"), "x")
coeffs_df$energy <- replace(coeffs_df$energy, which(coeffs_df$energy=="iU"), "u")
# Rearrange the energy factors to obtain our preferred ordering.
coeffs_df$energy <- as.factor(coeffs_df$energy)
energyLevels <- c(none="none", q="q", x="x", u="u")
for (lev in rev(energyLevels)) { coeffs_df$energy <- relevel(coeffs_df$energy, ref=lev) }

# Rearrange the energy factors to obtain our preferred ordering.
fitted_df$energy <- replace(fitted_df$energy, which(is.na(fitted_df$energy)), "none")
fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iQ"), "q")
fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iX"), "x")
fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iU"), "u")
fitted_df$energy <- as.factor(fitted_df$energy)
for (lev in rev(energyLevels)) { fitted_df$energy <- relevel(fitted_df$energy, ref=lev) }

>>>>

# Rearrange the country factors to obtain our preferred ordering.
# coeffs_df$country <- as.factor(coeffs_df$country)
# for (lev in rev(countryAbbrevs)) { coeffs_df$country <- relevel(coeffs_df$country, ref=lev) }
# Change the names of the energy factors to the desired names for the graph
# coeffs_df$energy <- replace(coeffs_df$energy, which(is.na(coeffs_df$energy)), "none")
# coeffs_df$energy <- replace(coeffs_df$energy, which(coeffs_df$energy=="iQ"), "q")
# coeffs_df$energy <- replace(coeffs_df$energy, which(coeffs_df$energy=="iX"), "x")
# coeffs_df$energy <- replace(coeffs_df$energy, which(coeffs_df$energy=="iU"), "u")
# Rearrange the energy factors to obtain our preferred ordering.
# coeffs_df$energy <- as.factor(coeffs_df$energy)
# energyLevels <- c(none="none", q="q", x="x", u="u")
# for (lev in rev(energyLevels)) { coeffs_df$energy <- relevel(coeffs_df$energy, ref=lev) }

# Rearrange the energy factors to obtain our preferred ordering.
# fitted_df$energy <- replace(fitted_df$energy, which(is.na(fitted_df$energy)), "none")
# fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iQ"), "q")
# fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iX"), "x")
# fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iU"), "u")
# fitted_df$energy <- as.factor(fitted_df$energy)
# for (lev in rev(energyLevels)) { fitted_df$energy <- relevel(fitted_df$energy, ref=lev) }

### 2014-05-18 Article/EconGrowth2.Rnw
Article now relies on re-leveling of factors by PostProcess.R

# Load coefficients from all models in one large data frame
# coeffs_df <- tbl_df( readRDS("../AllCoef.rda") )
coeffs_df <- tbl_df(AllCoef)
# Rearrange the country factors to obtain our preferred ordering.
coeffs_df$country <- as.factor(coeffs_df$country)
for (lev in rev(countryAbbrevs)) { coeffs_df$country <- relevel(coeffs_df$country, ref=lev) }
# Change the names of the energy factors to the names for the graph
coeffs_df$energy <- replace(coeffs_df$energy, which(is.na(coeffs_df$energy)), "none")
coeffs_df$energy <- replace(coeffs_df$energy, which(coeffs_df$energy=="iQ"), "q")
coeffs_df$energy <- replace(coeffs_df$energy, which(coeffs_df$energy=="iX"), "x")
coeffs_df$energy <- replace(coeffs_df$energy, which(coeffs_df$energy=="iU"), "u")
# Rearrange the energy factors to obtain our preferred ordering.
coeffs_df$energy <- as.factor(coeffs_df$energy)
energyLevels <- c(none="none", q="q", x="x", u="u")
for (lev in rev(energyLevels)) { coeffs_df$energy <- relevel(coeffs_df$energy, ref=lev) }

# Load fitted data from all models in one large data frame
# fitted_df <- tbl_df( readRDS("../AllFitted.rda") )
fitted_df <- tbl_df(AllFitted)
# Rearrange the energy factors to obtain our preferred ordering.
fitted_df$energy <- replace(fitted_df$energy, which(is.na(fitted_df$energy)), "none")
fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iQ"), "q")
fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iX"), "x")
fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iU"), "u")
fitted_df$energy <- as.factor(fitted_df$energy)
for (lev in rev(energyLevels)) { fitted_df$energy <- relevel(fitted_df$energy, ref=lev) }

@@

\twocolumn{}
<<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7, fig.cap="LINEX model (with energy) resampling results.">>=
linexCoeffsData <- filter(coeffs_df, model=="linex", energy=="q")
standardScatterPlot(data=linexCoeffsData, aes(a_0, c_t), facet_formula=country~energy, alpha=0.05) +
    labs(x=expression(a[0]), y=expression(c[t])) +
     scale_x_continuous(limits=c(-1, 2), breaks=c(-1, 0, 1.0, 2.0)) +
     scale_y_continuous(limits=c(0, 10), breaks=c(0, 5, 10))
@

<<LINEX_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7.1, fig.cap="LINEX fitted models.">>=
linexFittedData <- filter(fitted_df, model=="linex", energy=="q")
spaghettiPlot(data=linexFittedData, facet_formula=Country~energy, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@
\onecolumn{}

>>>>

# Load coefficients from all models in one large data frame
coeffs_df <- tbl_df(AllCoef)
# Load fitted data from all models in one large data frame
fitted_df <- tbl_df(AllFitted)

# Rearrange the country factors to obtain our preferred ordering.
# coeffs_df$country <- as.factor(coeffs_df$country)
# for (lev in rev(countryAbbrevs)) { coeffs_df$country <- relevel(coeffs_df$country, ref=lev) }
# Change the names of the energy factors to the names for the graph
# coeffs_df$energy <- replace(coeffs_df$energy, which(is.na(coeffs_df$energy)), "none")
# coeffs_df$energy <- replace(coeffs_df$energy, which(coeffs_df$energy=="iQ"), "q")
# coeffs_df$energy <- replace(coeffs_df$energy, which(coeffs_df$energy=="iX"), "x")
# coeffs_df$energy <- replace(coeffs_df$energy, which(coeffs_df$energy=="iU"), "u")
# Rearrange the energy factors to obtain our preferred ordering.
# coeffs_df$energy <- as.factor(coeffs_df$energy)
# energyLevels <- c(none="none", q="q", x="x", u="u")
# for (lev in rev(energyLevels)) { coeffs_df$energy <- relevel(coeffs_df$energy, ref=lev) }

# Rearrange the energy factors to obtain our preferred ordering.
# fitted_df$energy <- replace(fitted_df$energy, which(is.na(fitted_df$energy)), "none")
# fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iQ"), "q")
# fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iX"), "x")
# fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iU"), "u")
# fitted_df$energy <- as.factor(fitted_df$energy)
# for (lev in rev(energyLevels)) { fitted_df$energy <- relevel(fitted_df$energy, ref=lev) }

@@

\twocolumn{}
<<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7, fig.cap="LINEX model (with energy) resampling results.">>=
linexCoeffsData <- filter(coeffs_df, model=="linex", energy=="iQ")
standardScatterPlot(data=linexCoeffsData, aes(a_0, c_t), facet_formula=country~energy, alpha=0.05) +
    labs(x=expression(a[0]), y=expression(c[t])) +
     scale_x_continuous(limits=c(-1, 2), breaks=c(-1, 0, 1.0, 2.0)) +
     scale_y_continuous(limits=c(0, 10), breaks=c(0, 5, 10))
@

<<LINEX_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7.1, fig.cap="LINEX fitted models.">>=
linexFittedData <- filter(fitted_df, model=="linex", energy=="iQ")
spaghettiPlot(data=linexFittedData, facet_formula=Country~energy, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@
\onecolumn{}
